\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\contactinfo}[4]{%
  \begin{tabular}{@{}l}
    \faLinkedinSquare\hspace{0.3em}\href{#1}{LinkedIn}  \faGithubSquare\hspace{0.3em}\href{#2}{GitHub} \hspace{11.55cm}
    \faPhoneSquare\hspace{0.5em} \href{tel:#3}{#3} \\
  \end{tabular}
}
\begin{document}

\textbf{\LARGE{Subrat Yeeshukumar}} \hspace{7.74cm} \faEnvelopeSquare \hspace{0.5em}\href{mailto:shubrat.parth@gmail.com}{shubrat.parth@gmail.com}\\
\vspace{3pt}
\contactinfo
  {https://www.linkedin.com/in/subrat-yeeshu}
  {https://github.com/SubratYeeshu}
  {+91 9005921793}

  


%-----------EDUCATION-----------------
\section{\textbf{\textcolor{blue}{Education}}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology, Lucknow}{Lucknow}
      {Bachelor of Technology in Information Technology : CGPA: \textbf{7.96 / 10}}{July 2020 - Present}
      \resumeSubheading{Little Flower House, Varanasi}{Varanasi}{CBSE Class XII Aggregate Percentage : \textbf{93.4\%}}{2019 -2020}
  \resumeSubHeadingListEnd
%==============================Project===================

\section{\textbf{\textcolor{blue}{Projects}}}
  \resumeSubHeadingListStart
  \resumeItem{Flight Booking Management System \href{https://github.com/SubratYeeshu/Flight-Booking-Management-System}{\faExternalLink}}{A scalable and modular flight booking system with a robust tech stack, REST APIs, MVC architecture, and message queues for reliable communication between services.}
  % https://github.com/SubratYeeshu/FlightBookingManagementSystem
      \begin{itemize}
          \item[-] \textbf{Tech Stack} : JS, NodeJS, ExpressJS, MySql, Sequelize, Json Web Token (JWT), RabbitMQ, and AWS technologies
          \item[-] \textbf{MVC Architecture} : Pattern to ensure a structured and organized approach in the project development process.
          \item[-] \textbf{REST APIs} : Developed REST APIs for Flights and Search , Authorize and Authenticate, Booking Flight , and Reminder service as part of the microservices architecture, promoting scalability and modularity in the system. .
          \item[-] \textbf{Filters} : Implemented filters for Flights Service based on various categories, including price, time to reach, and number of stops, enhancing the search and filtering capabilities of the system.
          \item[-] \textbf{Message Queues} : Utilized message queues between Booking and Reminder service, ensuring seamless communication and reliability, even when the Reminder service was temporarily down.
      \end{itemize}
      
     \resumeItem{InterviewZenith \href{https://interviewzenith.netlify.app/}{\faExternalLink}} {An interactive MERN stack web app facilitating the sharing of interview experiences through CRUD operations}. 
     % https://interviewzenith.netlify.app/
      \begin{itemize}
          \item[-] \textbf{Tech Stack} : Javascript, React, NodeJS, ExpressJS, MongoDB.
          \item[-]\textbf{Nodemailer} : Used this npm package for implementing the features like forgot password and sending reply mails to contact form.
          
      \end{itemize}

      \resumeItem{Personal Portfolio \href{https://subrat-yeeshu.netlify.app/}{\faExternalLink}}{Portfolio website showcasing my professional achievements, skills, and projects.} 
     % https://subrat-yeeshu.netlify.app/
      \begin{itemize}
          \item[-] \textbf{Tech Stack} : HTML, CSS, Javascript
      \end{itemize}

 \resumeItemListEnd

%--------------------------------------Achivements
\section{\textbf{\textcolor{blue}{Achivements}}}
  \resumeSubHeadingListStart
  \begin{itemize}
  \item Solved over \textbf{1500+} Data Structures and Algorithms questions on various coding platforms.
  \item Leetcode \href{https://leetcode.com/Subrat_Yeeshu/}{\faExternalLink} Knight (Max Rating 1843)
  \item GFG \href{https://auth.geeksforgeeks.org/user/subrat_yeeshu/}{\faExternalLink} Ranked among the top 10 students of the institute
  \item Global Rank \textbf{709, 743, 1247, 1412} at various Leetcode Biweekly and Weekly Contests.
  \item \textbf{Hacktoberfest : }Collaborated and Contributed in Hacktoberfest 21, 22 as a Contributor by doing more than 20PR's and awarded all four badges.
  \item \textbf{Hacktoberfest : }Maintainer of a github repository having more than \textbf{10+} Contributor, and taught over \textbf{25+} students about Github and explained open source and analysed their contribution
        
  \item \textbf{Google Cloud 30 Days Challenge} : Completed both the tracks of the challenge.
\end{itemize}
      
 
     
 \resumeSubHeadingListEnd
%-----------------------------------------end project

%-----------Technical Skills And Coursework-----------------
\section{\textbf{\textcolor{blue}{Technical Skills And Coursework}}}
\resumeSubHeadingListStart
\begin{itemize}
     \item \textbf{Relevant Courses:} {Data Structures \& Algorithms, Operating System, DBMS, Object Oriented Programming, Computer Networks.}
    \item \textbf{Programming Languages:} {C, C++, JavaScript}
    \item\textbf{Technologies/ Frameworks/ Tools / Architecture:} {ReactJS, ExpressJS, MongoDB, Mongoose, Bootstrap, MySQL, Tailwind-CSS, JSON, Linux, Git/Github, VSCode}
      \end{itemize}
    \resumeSubHeadingListEnd
    
    \section{\textbf{\textcolor{blue}{Soft Skills}}}
    \begin{itemize}
    \item {Team Management / Planning / Collaboration / Problem Solving / Leadership Principles}
\end{itemize}

  
% {\fontsize{5}{5}\selectfont\color{white}
% testing software engineer problem solving crm computer science cloud computing cloud ai testing problem solving, problem solving writing
% solutions software site reliability security product playbook migration
% machine learning lean industry trends http frontend enterprise engineer documentation design patterns data engineer collaborate clean backlog backend atlassian application agile security product collaborate backend
% atlassian
% }


\end{document}
